Ecological Traitdata Standard

### 2017-05-12 docs/traitdatastandard.Rmd
move to docs folder

---
title: "Ecological Traitdata Standard"
author: "Florian D. Schneider, Nadja Simons, Caterina Penone, Andreas Ostrowski"
date: "12 Mai 2017"
output: html_document
---

@@

```{r, results = 'asis', echo = FALSE}
library(data.table)
library(knitr)
library(pander)
glossary <- read.csv("template_glossary.csv")

>>>>

---
title: "Ecological Traitdata Standard"
author: "Florian D. Schneider, Nadja Simons, Caterina Penone, Andreas Ostrowski"
date: "12 Mai 2017"
output: 
  html_document: 
    keep_md: yes
---

@@

```{r, results = 'asis', echo = FALSE}
library(data.table)
library(knitr)
library(pander)
glossary <- read.csv("../template_glossary.csv")
